Application of an immersed boundary technique to wildfire simulation over complex terrains

### 2020-03-06 Vanella_Article_Atmosphere_2020.tex
Atmosphere .tex : My changes to Title, abstract.

%=================================================================
% Full title of the paper (Capitalized)
\Title{Modeling Terrain using an Immersed Boundary Method}

@@

\abstract{A method for simulating the spread of wildfire over complex terrain is presented. An immersed boundary method (IBM) is used to render the complex terrain on a rectilinear Cartesian grid. Fire spread is modeled using one of three basic approaches: (1) representing the vegetation as a collection of Lagrangian particles, (2) representing the vegetation as a semi-porous boundary, and (3) representing the fire spread using a level set technique in which the fire spreads as a function of terrain, vegetation type, and wind speed.}

>>>>

%=================================================================
% Full title of the paper (Capitalized)
\Title{Application of an immersed boundary technique to wildfire simulation over complex terrains}

@@

\abstract{A method for the large eddy simulation (LES) of wildfire spread over complex terrains is presented. In this scheme, a cut-cell immersed boundary method (IBM) is used to render the complex terrain, defined by a tessellation, on a rectilinear Cartesian grid. Discretization of scalar transport equations for chemical species is done via a finite volume scheme on cut-cells defined by the intersection of the terrain and Cartesian cells. Momentum transport and heat transfer close to the immersed terrain are handled using a dynamic wall model and direct forcing IBM. Further, atmospheric wind conditions are specified using a mean wind forcing concept. Fire spread is modeled using one of three basic approaches: (1) representing the vegetation as a collection of Lagrangian particles, (2) representing the vegetation as a semi-porous boundary, and (3) representing the fire spread using a level set technique in which the fire spreads as a function of terrain, vegetation type, and wind speed. Several test and validation cases are reported to demonstrate the capabilities of this novel wildfire simulation methodology.}
